Predicting Tags for StackOverflow Posts

### 2013-02-11 stackExchange/writeups/iccm-2013/writeup.tex
foo
Former-commit-id: d82f8f9fa1cb3a0581a678ad989b764b19aafad4 [formerly ff032473ca3222c7c4bdc540623b737201b95309]
Former-commit-id: 05c9ffbce4b58bfe2edcbc6c295ae7c37ee51b08

In order to formally test model performance and to calibrate model parameters, a calibration run using \num{1000} posts was performed.
For the calibration run, the category prediction (chosen or not chosen tag for a post) was regressed on base-level activation, spreading activation for title and body, and post offset.
Best-fit coefficients for each model component and formal statistical measurements are included in Tables \ref{tab:coeffs} and \ref{tab:fits} respectively.

>>>>

In order to formally test model performance and to calibrate model parameters, a calibration run using \num{1000} posts was performed.
For the calibration run, the category prediction (chosen or not chosen tag for a post) was regressed on base-level activation, spreading activation for title and body, and post offset.
However using a single run of the \num{1000} posts was insufficient because there are two model components that require prior estimates of coefficients:
The offset measure to determine the top-five tags and associated activation and the sampling technique used to pick a representative set of tags for each post.
So model calibration was performed four times, where the coefficients from the previous run were used as estimates of coefficients for the next run.
The coefficients converged on best-fit values quickly (running just two times would have sufficed), and did not show any sign of instability with the iterative technique.
The final best-fit coefficients for each model component and formal statistical measurements are included in Tables \ref{tab:coeffs} and \ref{tab:fits} respectively.
